Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-08 tex/body.tex
minor

However, under the assumption that the function definitions in
$\sfundefs{\Sigma}$ are admissible, %we claim that
$\conv(\varphi)$ is equisatisfiable with $\varphi$ for any input $\varphi$.
%\ct{Must define "equisatisfiable".
%What we mean here is a weak form of satisfiability, we could instead say that
%$\conv(\varphi)$ is $T$-satisfiable iff $\varphi$ is $T$-satisfiable.
%} 
%\jb{We do define it, even it is weak form.}
The intuition is that the
interpretation of a term such as $\con{s}( -1 )$ in the previous example is not
relevant to the satisfiability of formula~(\ref{eq:ex-before}). Thus, a
satisfiable or unsatisfiable response from an SMT solver on input $\conv(
\varphi )$ implies the existence or nonexistence of a model for
$\varphi$. Moreover, the models of $\conv( \varphi )$ contain
pertinent information regarding the models of $\varphi$. For example, the model
$\I$ for formula~(\ref{eq:ex-after}) given above interprets $\con{c}$ as $14$
and $\con{s}(n) = \sum_{i=1}^n i$ for $0 \le n \le 14$,
and there exists a model of formula~(\ref{eq:ex-before}) that also interprets
$\con{c}$ and and $\con{s}(n)$ in the same way (for $0 \le n \le 14$).
In general, there exists a model of $\varphi$ that
coincides with each model of $\conv( \varphi )$ on its interpretation of all
functions in $\sfuns{\Sigma} - \sfundefs{\Sigma}$, i.e., $\{
\con{s} \}$ in the example. Furthermore, the model of $\conv( \varphi )$ will
also give correct information for the defined functions at all points belonging
to the domains of the corresponding abstract types. This can sometimes help
users debug their specifications.

>>>>

However, under the assumption that the function definitions in
$\sfundefs{\Sigma}$ are admissible, %we claim that
$\conv(\varphi)$ is equisatisfiable with $\varphi$ for any input $\varphi$.
%\ct{Must define "equisatisfiable".
%What we mean here is a weak form of satisfiability, we could instead say that
%$\conv(\varphi)$ is $T$-satisfiable iff $\varphi$ is $T$-satisfiable.
%} 
%\jb{We do define it, even it is weak form.}
The intuition is that the
interpretation of a term such as $\con{s}( -1 )$ in the previous example is not
relevant to the satisfiability of formula~(\ref{eq:ex-before}). Thus, a
satisfiable or unsatisfiable response from an SMT solver on input $\conv(
\varphi )$ implies the existence or nonexistence of a model for
$\varphi$. Moreover, the models of $\conv( \varphi )$ contain
pertinent information regarding the models of $\varphi$. For example, the model
$\I$ for formula~(\ref{eq:ex-after}) given above interprets $\con{c}$ as $14$
and $\con{s}(n)$ as $\sum_{i=1}^n i$ for $0 \le n \le 14$,
and there exists a model of formula~(\ref{eq:ex-before}) that also interprets
$\con{c}$ and and $\con{s}(n)$ in the same way (for $0 \le n \le 14$).
In general, there exists a model of $\varphi$ that
coincides with each model of $\conv( \varphi )$ on its interpretation of all
functions in $\sfuns{\Sigma} - \sfundefs{\Sigma}$, i.e., $\{
\con{s} \}$ in the example. Furthermore, the model of $\conv( \varphi )$ will
also give correct information for the defined functions at all points belonging
to the domains of the corresponding abstract types. This can sometimes help
users debug their specifications.
